Supplementary Information

### 2015-07-01 manuscript/supplement.tex
working on adding in big table

% some cheats to reduce the need to type complicated bits and pieces
\newcommand{\expect}[1]{\left\langle #1 \right\rangle}
\newcommand{\etal}{\textit{et al.\ }}

\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{S\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{S\arabic{figure}}%
     }

% the abstract formatting
\newenvironment{sciabstract}{%
\begin{quote} \bf}
{\end{quote}}

@@

  We combined published food webs from~\citet{GlobaWeb},~\citet{Riede2011},
  and~\citet{Dunne2013}. Of the 358 food webs available
  from~\citet{Globalweb}, 59 were rejected because their original source was
  unpublished or could not be retrieved. We further eliminated 13 source or
  sink webs (which describe feeding links flowing from or to a particular
  resource or top predator rather than the interactions of an entire
  community), 8 plant-pollinator webs, 33 host-parasitoid webs, and 2 networks
  describing competitive interactions. Finally, we eliminated 2 webs
  describing  inferred interactions in an extinct community, 10 ``generalized
  schemes'' that were not based on direct field data, and 4 webs where it was
  not clear which of several described study sites were used to construct the
  food web (and therefore the latitude of the food web could not be
  included). This left us with 226 webs from~\citet{GlobalWeb}.

@@

 See Table S1 for a list of rejected webs and reasons for their
  exclusion.

>>>>

% some cheats to reduce the need to type complicated bits and pieces
\newcommand{\expect}[1]{\left\langle #1 \right\rangle}
\newcommand{\etal}{\textit{et al.\ }

\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{S\arabic{table}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{S\arabic{figure}%
     }

% the abstract formatting
\newenvironment{sciabstract}{%
\begin{quote} \bf}
{\end{quote}

@@

  We combined published food webs from~\citet{GlobalWeb},~\citet{Riede2011},
  and~\citet{Dunne2013}. Of the 358 food webs available
  from~\citet{GlobalWeb}, 59 were rejected because their original source was
  unpublished or could not be retrieved. We further eliminated 13 source or
  sink webs (which describe feeding links flowing from or to a particular
  resource or top predator rather than the interactions of an entire
  community), 8 plant-pollinator webs, 33 host-parasitoid webs, and 2 networks
  describing competitive interactions. Finally, we eliminated 2 webs
  describing  inferred interactions in an extinct community, 10 ``generalized
  schemes'' that were not based on direct field data, and 4 webs where it was
  not clear which of several described study sites were used to construct the
  food web (and therefore the latitude of the food web could not be
  included). This left us with 226 webs from~\citet{GlobalWeb}.

@@

 See Table~\ref{S1} for a list of rejected webs and reasons for their
  exclusion.

\newpage
\begin{landscape}

  \begin{table}[h!]
  \centering
  \caption{Sources of food webs considered for use in this study. ``Collection" indicates the direct source of the
  food web (i.e., where the interaction matrix was obtained) while ``Original source" indicates the original publication
  of the food web. We also show the ecosystem type, country of origin, and latitude for each food web, as well as whether
  it was ultimately included in the study.  }
  \label{S1}
% Table generated by Excel2LaTeX from sheet 'Sheet1'
    \begin{tabular}{rrrrrrrrr}
      \hline
      Web ID & Collection & Original Source & Location & Ecosystem & Latitude(degrees) & Used  & Reason for rejection & Notes \\
      \hline
      Alamitos & ~\citet{Riede2011} & ~\citet{Harrison1995} & USA   & stream & 37,12,25 N & Yes   &       &  \\
      Alford & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 44,15,41.59 N & Yes   &       &  \\
      Beaver & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 44,18,58.13 N & Yes   &       &  \\
      Bere  & ~\citet{Riede2011} & ~\citet{Woodward2008} & England & stream & 50,45,7 N & Yes   &       &  \\
      Bridge & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 44,09,42.66 N & Yes   &       &  \\
      Broad & ~\citet{Riede2011} & ~\citet{Townsend1998} & New Zealand & stream & 45.896938 S & Yes   &       &  \\
      Broadstone & ~\citet{Riede2011} & ~\citet{Woodward2005} & stream & stream & 51,01,05 N & Yes   &       &  \\
      Calero & ~\citet{Riede2011} & ~\citet{Harrison1995} & USA   & stream & 37,11,09 - 20 N & Yes   &       &  \\
      Canton & ~\citet{Riede2011} & ~\citet{Townsend1998} & New Zealand & stream & 45.752 S & No    & Duplicated in GlobalWeb (web 235) &  \\
      Carpinteria2006 & ~\citet{Riede2011} & ~\citet{Lafferty2006} & USA   & estuary & 34.41 - 34.40 N & Yes   &       &  \\
      Chub  & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 43,31,39.36 N & Yes   &       &  \\
      Coachella & ~\citet{Riede2011} & ~\citet{Polis1991a} & desert & terrestrial & 33,54 N & Yes   &       &  \\
      Connery & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 44,18,42.10 N & Yes   &       &  \\
      Corte & ~\citet{Riede2011} & ~\citet{Harrison1995} & USA   & stream & 37,56,28 - 37,57,39 N & Yes   &       &  \\
      Coyote & ~\citet{Riede2011} & ~\citet{Harrison1995} & USA   & stream & 37,53,11.66 - 37,53,17.06 N & Yes   &       &  \\
      German & ~\citet{Riede2011} & ~\citet{Townsend1998} & New Zealand & stream & 44.97 S & No    & Duplicated in GlobalWeb (web 227) &  \\
      GrandeCl & ~\citet{Riede2011} & ~\citet{CattinBlandenier2004} & wetland & terrestrial & 46,47,09 N & Yes   &       &  \\
      GrandeSc & ~\citet{Riede2011} & ~\citet{CattinBlandenier2004} & wetland & terrestrial & 46,47,09 N & Yes   &       &  \\
      Guadalupe & ~\citet{Riede2011} & ~\citet{Harrison1995} & USA   & stream & 37,27,54 - 37,21,17 N & Yes   &       &  \\
      Hainich   & ~\citet{Riede2011} & Unpublished & Germany & terrestrial &       & No    & Could not locate original source &  \\
      LittleKyeBurn & ~\citet{Riede2011} & ~\citet{Townsend1998} & New Zealand & stream & 45 S  & No    & Duplicated in GlobalWeb (web 230) &  \\
      LittleRock & ~\citet{Riede2011} & ~\citet{Martinez1991} & USA   & lake  & 45,44,07.94 N & Yes   &       &  \\
      Mondego & ~\citet{Riede2011} & ~\citet{Patricio2006} & Portugal & estuary & 40,08 N & Yes   &       &  \\
      Montane Forest, Arizona & ~\citet{Riede2011} & ~\citet{Rasmussen1941} & USA   & terrestrial & 36,5-37 N & No    & Duplicated in GlobalWeb (web60) &  \\
      Reef  & ~\citet{Riede2011} & ~\citet{Opitz1996} & Caribbean & marine & 18,29 - 17,53 N & Yes   &       &  \\
      Sierra & ~\citet{Riede2011} & ~\citet{Brose2005} & USA   & lake  & 36,50 - 37,02 N & Yes   &       &  \\
      SimberloffE1 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 24,40,37.29 N & Yes   &       &  \\
      SimberloffE2 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 24,40,33 N & Yes   &       &  \\
      SimberloffE3 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 24,41,23.82 N & Yes   &       &  \\
      SimberloffE7 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 25,15 N & Yes   &       &  \\
      SimberloffE9 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 25,01,59.64 - 25,02,55.44 N & Yes   &       &  \\
      SimberloffST2 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 24,36,16 N & Yes   &       &  \\
      Skipwith & ~\citet{Riede2011} & ~\citet{Warren1989} & England & lake  & 53,40 N & Yes   &       &  \\
      Stink & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 43,37,55.88 N & Yes   &       &  \\
      StMarks & ~\citet{Riede2011} & ~\citet{Christian1999} & USA   & estuary & 30,05 N & No    & Duplicated in GlobalWeb (web 288) &  \\
      Stony  & ~\citet{Riede2011} & ~\citet{Townsend1998} & New Zealand & stream & 45.58 S & No    & Duplicated in GlobalWeb (web 231) &  \\
      TreleaseWoods & ~\citet{Riede2011} & \multicolumn{1}{l}{~\citet{Twomey1945} & USA   & terrestrial & 40,09,47 N & No    & Duplicated in GlobalWeb (web 59) &  \\
      Tuesday & ~\citet{Riede2011} & ~\citet{Jonsson2005} & USA   & lake  & 46,13 N & Yes   &       &  \\
      Weddell Sea & ~\citet{Riede2011} & ~\citet{Brose2005} & Antarctica & marine & 58,20.8 - 60,10.4 S & No    & Duplicated in GlobalWeb (web 341) &  \\
      Ythan & ~\citet{Riede2011} & ~\citet{Huxham1996} & UK    & marine &       & No    & Duplicated in Dunne (YthanDunne) &  \\
      BahiaDunne & ~\citet{Dunne2013} & ~\citet{Hechinger2011} & Mexico & estuary & 30.43 - 30.46 N & Yes   &       & Parasites removed \\
      CarpinteriaDunne & ~\citet{Dunne2013} & ~\citet{Hechinger2011} & USA   & estuary & 34.41 - 34.40 N & Yes   &       & Parasites removed \\
      EsteroDunne & ~\citet{Dunne2013} & ~\citet{Hechinger2011} & Mexico & estuary & 31.78 - 31.69 N & Yes   &       & Parasites removed \\
      FjordDunne & ~\citet{Dunne2013} & ~\citet{Zander2011} & Germany & estuary & 54.92 - 54.75 N & Yes   &       & Parasites removed \\
      OtagoDunne & ~\citet{Dunne2013} & ~\citet{Mouritsen2011} & New Zealand & estuary & 45.78 - 45.88 S & Yes   &       & Parasites removed \\
      SyltDunne & ~\citet{Dunne2013} & ~\citet{Thieltges2011} & Denmark & estuary & 54.83 - 55.12 N & Yes   &       & Parasites removed \\
      YthanDunne & ~\citet{Dunne2013} & ~\citet{Huxham1996} & Scotland & estuary & 57,18,32 N & Yes   &       & Parasites removed \\
      1     & ~\citet{GlobalWeb} & ~\citet{Qazim1970} & India & estuary &       & No    & Could not locate original source &  \\
      2     & ~\citet{GlobalWeb} & ~\citet{Day1967} & South Africa & estuary &       & No    & Could not locate original source &  \\
      3     & ~\citet{GlobalWeb} & ~\citet{Woodwell1967} & USA   & estuary & 41,03,11 N & Yes   &       &  \\
      4     & ~\citet{GlobalWeb} & ~\citet{Johnston1956} & USA   & estuary &       & No    & Sink web &  \\
      5     & ~\citet{GlobalWeb} & ~\citet{Teal1962} & USA   & estuary & 31,28,38 N & Yes   &       &  \\
      6     & ~\citet{GlobalWeb} & ~\citet{MacGinitie1935} & USA   & estuary & 36,48,18 N & Yes   &       &  \\
      7     & ~\citet{GlobalWeb} & ~\citet{Kremer1978} & USA   & marine & 41,45 - 41,30 N & Yes   &       &  \\
      8     & ~\citet{GlobalWeb} & ~\citet{Nixon1973} & USA   & estuary & 41,33,00 N & Yes   &       &  \\
      9     & ~\citet{GlobalWeb} & ~\citet{Kitching1967} & Ireland & stream &       & No    & Could not locate original source &  \\
      10    & ~\citet{GlobalWeb} & ~\citet{Menge1976} & USA   & marine & 41 - 47 N & Yes   &       &  \\
      11    & ~\citet{GlobalWeb} & ~\citet{Menge1976} & USA   & marine & 41 - 47 N & Yes   &       &  \\
      12    & ~\citet{GlobalWeb} & ~\citet{Menge1976} & USA   & marine & 45,45 - 49 N & Yes   &       &  \\
      13    & ~\citet{GlobalWeb} & ~\citet{Menge1976} & USA   & marine & 45,45 - 49 N & Yes   &       &  \\
      14    & ~\citet{GlobalWeb} & ~\citet{Walsh1967} & Hawaii & estuary & 21,26,09 N & No    & Could not locate original source &  \\
      15    & ~\citet{GlobalWeb} & ~\citet{Walsh1967} & Hawaii & estuary & 21,26,09 N & No    & Could not locate original source &  \\
      16    & ~\citet{GlobalWeb} & ~\citet{Copeland1974} & USA   & estuary &       & No    & Could not locate original source &  \\
      17    & ~\citet{GlobalWeb} & ~\citet{Hiatt1960} & Marshall Islands - Pacific Ocean & marine & 4,30 - 15 N & No    & Generalized scheme &  \\
      18    & ~\citet{GlobalWeb} & ~\citet{Niering1963a} & Polynesia & terrestrial & 1,01,29 - 1,06,23 N & Yes   &       &  \\
      19    & ~\citet{GlobalWeb} & ~\citet{Brooks1963} & USA   & lake &       & No    & Could not locate original source &  \\
      20    & ~\citet{GlobalWeb} & ~\citet{Knox1970} & Antarctica & terrestrial &       & No    & Could not locate original source &  \\
      21    & ~\citet{GlobalWeb} & ~\citet{Patten1979} & Antarctica & marine & 70-85 S & Yes   &       &  \\
      22    & ~\citet{GlobalWeb} & ~\citet{Summerhayes1923} & Norway & terrestrial & 74,27,54 N & Yes   &       &  \\
      23    & ~\citet{GlobalWeb} & ~\citet{Bird1930} & Canada & terrestrial & 50,25,17 N & Yes   &       &  \\
      24    & ~\citet{GlobalWeb} & ~\citet{Bird1930} & Canada & terrestrial & 50,25,17 N & Yes   &       &  \\
      25    & ~\citet{GlobalWeb} & ~\citet{Bird1930} & Canada & terrestrial & 50,25,17 N & Yes   &       &  \\
      26    & ~\citet{GlobalWeb} & ~\citet{Bird1930} & Canada & terrestrial & 50,25,17 N & Yes   &       &  \\
      27    & ~\citet{GlobalWeb} & ~\citet{Varley1970} & England & terrestrial &       & No    & Could not locate original source &  \\
      28    & ~\citet{GlobalWeb} & ~\citet{Paviour-Smith1956} & New Zealand & estuary & 45,51,30 S & Yes   &       &  \\
      29    & ~\citet{GlobalWeb} & ~\citet{Dunbar1953} & Arctic seas & marine &       & No    & Generalized scheme &  \\
      30    & ~\citet{GlobalWeb} & ~\citet{Mackintosh1964} & Antarctica & marine &       & No    & Generalized scheme &  \\
      31    & ~\citet{GlobalWeb} & ~\citet{Petipa1970} & Black Sea & marine &       & No    & Could not locate original source &  \\
      32    & ~\citet{GlobalWeb} & ~\citet{Petipa1970} & Black Sea & marine &       & No    & Could not locate original source &  \\
      33    & ~\citet{GlobalWeb} & ~\citet{Fryer1959} & Malawi & lake & 11,36,39 S & Yes   &       &  \\
      34    & ~\citet{GlobalWeb} & ~\citet{Jones1949} & UK    & stream & 51,41 - 51,55 N & Yes   &       &  \\
      35    & ~\citet{GlobalWeb} & ~\citet{Minshall1967} & USA   & stream & 37,18,26 N & Yes   &       &  \\
      36    & ~\citet{GlobalWeb} & ~\citet{Walsh1967} & Hawaii & estuary & 21,26,09 N & No    & Could not locate original source &  \\
      37    & ~\citet{GlobalWeb} & ~\citet{Clarke1967} & USA   & marine & 41,02,49 N & Yes   &       &  \\
      38    & ~\citet{GlobalWeb} & ~\citet{Fryer1959} & Malawi & lake & 11,36,39 S & Yes   &       &  \\
      39    & ~\citet{GlobalWeb} & ~\citet{Fryer1959} & Malawi & lake & 11,36,39 S & Yes   &       &  \\
      40    & ~\citet{GlobalWeb} & ~\citet{Harrison1962} & Malaysia & terrestrial &       & No    & Generalized scheme &  \\
      41    & ~\citet{GlobalWeb} & ~\citet{Parin1970} & Israel & marine &       & No    & Could not locate original source &  \\
      42    & ~\citet{GlobalWeb} & ~\citet{Vinogradov1978} & Pacific Ocean & marine &       & No    & Study site unclear &  \\
      43    & ~\citet{GlobalWeb} & ~\citet{Rosenthal1974} & USA   & marine & 32,57 N & Yes   &       &  \\
      44    & ~\citet{GlobalWeb} & ~\citet{Yanez1978} & Mexico & marine & 17,26,21 N & Yes   &       &  \\
      45    & ~\citet{GlobalWeb} & ~\citet{Tilly1968} & USA   & stream & 41,22,55 N & Yes   &       &  \\
      46    & ~\citet{GlobalWeb} & ~\citet{Patten1975} & USA   & lake & 33,54 N & Yes   &       &  \\
      47    & ~\citet{GlobalWeb} & ~\citet{Harris1980} & USA   & lake &       & No    & Study site unclear &  \\
      48    & ~\citet{GlobalWeb} & ~\citet{Simenstad1978} & USA   & marine &       & No    & Extinct species &  \\
      49    & ~\citet{GlobalWeb} & ~\citet{Simenstad1978} & USA   & marine &       & No    & Extinct species &  \\
      50    & ~\citet{GlobalWeb} & ~\citet{Nybakken1982} & USA   & marine &       & No    & Generalized scheme &  \\
      51    & ~\citet{GlobalWeb} & ~\citet{Dexter1947} & USA   & marine & 42,38,56 N & Yes   &       &  \\
      52    & ~\citet{GlobalWeb} & ~\citet{Paine1980a} & USA   & marine & 58,27 N & Yes   &       &  \\
      53    & ~\citet{GlobalWeb} & ~\citet{Paine1980a} & USA   & marine & 48,19 - 48,37 N & Yes   &       &  \\
      54    & ~\citet{GlobalWeb} & Unpublished & Barbados & marine &       & No    & Unpublished &  \\
      55    & ~\citet{GlobalWeb} & ~\citet{Milne1972} & Scotland & estuary &       & No    & Could not locate original source &  \\
      56    & ~\citet{GlobalWeb} & ~\citet{Milne1972} & Scotland & estuary &       & No    & Could not locate original source &  \\
      57    & ~\citet{GlobalWeb} & ~\citet{Yanez1978} & Mexico & marine & 17,26,21 N & Yes   &       &  \\
      58    & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & Russia & lake & 51,46 N & Yes   &       &  \\
      59    & ~\citet{GlobalWeb} & ~\citet{Twomey1945} & USA   & terrestrial & 40,09,47 N & Yes   &       &  \\
      60    & ~\citet{GlobalWeb} & ~\citet{Rasmussen1941} & USA   & terrestrial & 36,5-37 N & Yes   &       &  \\
      61    & ~\citet{GlobalWeb} & ~\citet{Summerhayes1928} & Norway & terrestrial & 77,52,30 N & Yes   &       &  \\
      62    & ~\citet{GlobalWeb} & ~\citet{Summerhayes1928} & Norway & terrestrial & 77,52,30 N & Yes   &       &  \\
      63    & ~\citet{GlobalWeb} & ~\citet{Jones1950} & UK    & stream & 52,25,08 N & Yes   &       &  \\
      64    & ~\citet{GlobalWeb} & ~\citet{Cummins1966} & USA   & stream & 41,39,33 N & Yes   &       &  \\
      65    & ~\citet{GlobalWeb} & ~\citet{Tsuda1972} & Japan & stream & 34,21,20 - 34,23,21 N & Yes   &       &  \\
      66    & ~\citet{GlobalWeb} & ~\citet{Mann1972a} & England & stream & 51,30 N & Yes   &       &  \\
      67    & ~\citet{GlobalWeb} & ~\citet{Carlson1968} & USA   & river} & 40,24,16 N & Yes   &       &  \\
      68    & ~\citet{GlobalWeb} & ~\citet{Morgan1972} & Scotland & lake &       & No    & Could not locate original source &  \\
      69    & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & Portugal & estuary &       & No    & Could not locate original source &  \\
      70    & ~\citet{GlobalWeb} & ~\citet{Kemp1977} & USA   & estuary & 28,54,08 N & Yes   &       &  \\
      71    & ~\citet{GlobalWeb} & ~\citet{Sorokin1972} & Russia & lake & 48,00 N & Yes   &       &  \\
      72    & ~\citet{GlobalWeb} & ~\citet{Baril1983} & Canada & lake & 46,02 N & Yes   &       &  \\
      73    & ~\citet{GlobalWeb} & ~\citet{Schiemer1979} & Austria & lake &       & No    & Could not locate original source &  \\
      74    & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & South Africa & marine & 34,15,00 S & Yes   &       &  \\
      75    & ~\citet{GlobalWeb} & ~\citet{Pechlaner1972} & Austria & lake & 47,11 N & Yes   &       &  \\
      76    & ~\citet{GlobalWeb} & ~\citet{Schiemer1979} & Austria & lake & 47,42 - 47,54 N & Yes   &       &  \\
      77    & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & Ethiopia & lake &       & No    & Could not locate original source &  \\
      78    & ~\citet{GlobalWeb} & ~\citet{Burgis1972} & Uganda & lake & 0     & Yes   &       &  \\
      79    & ~\citet{GlobalWeb} & ~\citet{Sarvala1974} & Finland & lake &       & No    & Could not locate original source &  \\
      80    & ~\citet{GlobalWeb} & ~\citet{Sarvala1974} & Finland & lake &       & No    & Could not locate original source &  \\
      81    & ~\citet{GlobalWeb} & ~\citet{Hatanaka1977} & Japan & marine &       & No    & Could not locate original source &  \\
      82    & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & France & marine &       & No    & Could not locate original source &  \\
      83    & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & Finland & lake &       & No    & Could not locate original source &  \\
      84    & ~\citet{GlobalWeb} & ~\citet{Wilbur1972} & USA   & lake & 42,28,42 N & Yes   &       &  \\
      85    & ~\citet{GlobalWeb} & ~\citet{Mizuno1982} & Malaysia & lake &       & No    & Could not locate original source &  \\
      86    & ~\citet{GlobalWeb} & ~\citet{Hogetsu1979} & Japan & marine & 34,36 - 35,38 N & Yes   &       &  \\
      87    & ~\citet{GlobalWeb} & ~\citet{Bradstreet1982} & Canada & terrestrial & 72,46,34.95 N & Yes   &       &  \\
      88    & ~\citet{GlobalWeb} & ~\citet{Kuusela1980} & Finland & stream &       & No    & Could not locate original source &  \\
      89    & ~\citet{GlobalWeb} & ~\citet{Hartley1948} & England & stream & 52,13 N & Yes   &       &  \\
      91    & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & Japan & terrestrial &       & No    & Could not locate original source &  \\
      92    & ~\citet{GlobalWeb} & ~\citet{Swan1961} & Tibet & terrestrial &       & No    & Generalized scheme &  \\
      93    & ~\citet{GlobalWeb} & ~\citet{Pattie1966} & USA   & terrestrial & 45 N  & Yes   &       &  \\
      94    & ~\citet{GlobalWeb} & ~\citet{Brown1971} & USA   & terrestrial &       & No    & Could not locate original source &  \\
      95    & ~\citet{GlobalWeb} & ~\citet{Brown1975} & USA   & terrestrial & 70,11,14.18 N & Yes   &       &  \\
      96    & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & Russia & terrestrial &       & No    & Could not locate original source &  \\
      97    & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & Russia & terrestrial &       & No    & Could not locate original source &  \\
      98    & ~\citet{GlobalWeb} & ~\citet{Holm1980} & Namibia & terrestrial &       & No    & Could not locate original source &  \\
      99    & ~\citet{GlobalWeb} & ~\citet{Howes1954} & USA   & terrestrial & 32,36 N & Yes   &       &  \\
      100   & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & India & terrestrial &       & No    & Could not locate original source &  \\
      101   & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & France & lake  &       & No    & Could not locate original source &  \\
      102   & ~\citet{GlobalWeb} & ~\citet{Shushkina1973} & Pacific Ocean & marine & 10 S - 15 N & Yes   &       &  \\
      103   & ~\citet{GlobalWeb} & ~\citet{Petipa1979} & Pacific Ocean & marine &       & No    & Generalized scheme &  \\
      104   & ~\citet{GlobalWeb} & ~\citet{Menge1976} & Panama & marine & 4,48,04 N & Yes   &       &  \\
      105   & ~\citet{GlobalWeb} & ~\citet{Edwards1982} & USA & marine & 42,40 N & Yes   &       &  \\
      106   & ~\citet{GlobalWeb} & ~\citet{Glynn1965} & USA & marine &       & No    & Could not locate original source &  \\
      107   & ~\citet{GlobalWeb} & ~\citet{Peterson1979} & USA & marine & 39,52,02 N & Yes   &       &  \\
      108   & ~\citet{GlobalWeb} & ~\citet{Hewatt1937} & USA & marine & 36,37 N & Yes   &       &  \\
      109   & ~\citet{GlobalWeb} & ~\citet{Castilla1981} & Chile} & marine &       & No    & Could not locate original source &  \\
      110   & ~\citet{GlobalWeb} & ~\citet{Dexter1947} & USA & marine & 42,38,56 N & Yes   &       &  \\
      111   & ~\citet{GlobalWeb} & ~\citet{Dexter1947} & USA & marine & 42,38,56 N & Yes   &       &  \\
      112   & ~\citet{GlobalWeb} & ~\citet{Dexter1947} & USA & marine & 42,38,56 N & Yes   &       &  \\
      113   & ~\citet{GlobalWeb} & ~\citet{Dexter1947} & USA & marine & 42,38,56 N & Yes   &       &  \\
      114   & ~\citet{GlobalWeb} & ~\citet{Marshall1982} & Zimbabwe & lake  & 17,54,11.90 S & Yes   &       &  \\
      115   & ~\citet{GlobalWeb} & ~\citet{Koepcke1952} & Peru} & marine &       & No    & Could not locate original source &  \\
      116   & ~\citet{GlobalWeb} & ~\citet{Hurlbert1972} & USA & lake  & 35,09,19 S & Yes   &       &  \\
      117   & ~\citet{GlobalWeb} & ~\citet{Zaret1973} & Panama & lake  & 9,11,31.50 N & Yes   &       &  \\
      118   & ~\citet{GlobalWeb} & ~\citet{Bindloss1972} & UK & lake  & 56,41,18.71 N & Yes   &       &  \\
      119   & ~\citet{GlobalWeb} & ~\citet{Mann1972} & UK & stream & 51,27 N & Yes   &       &  \\
      120   & ~\citet{GlobalWeb} & ~\citet{Moriarty1973} & Uganda & lake  & 0,00,58 N & Yes   &       &  \\
      121   & ~\citet{GlobalWeb} & ~\citet{VanEs1977} & Germany & estuary & 53,20 - 53,15 N & Yes   &       &  \\
      122   & ~\citet{GlobalWeb} & ~\citet{Nixon1973} & USA & estuary & 41,33,04 N & Yes   &       &  \\
      123   & ~\citet{GlobalWeb} & ~\citet{Harris1972} & USA & terrestrial & 40,45,28 N & Yes   &       &  \\
      124   & ~\citet{GlobalWeb} & ~\citet{Collins1976} & USA & stream & 44,34 N & Yes   &       &  \\
      125   & ~\citet{GlobalWeb} & ~\citet{Landry1977} & Unspecified & marine &       & No    & Generalized scheme &  \\
      126   & ~\citet{GlobalWeb} & ~\citet{Larsson1978} & Norway & lake  & 61,26,00 N & Yes   &       &  \\
      127   & ~\citet{GlobalWeb} & ~\citet{Beaver1979} & Malaysia & lake  &       & No    & Could not locate original source &  \\
      128   & ~\citet{GlobalWeb} & ~\citet{Beaver1979} & Malaysia & lake  &       & No    & Could not locate original source &  \\
      129   & ~\citet{GlobalWeb} & Unpublished & Unspecified & terrestrial &       & No    & Unpublished &  \\
      130   & ~\citet{GlobalWeb} & ~\citet{Odum1975} & USA & estuary & 27,12 N & Yes   &       &  \\
      131   & ~\citet{GlobalWeb} & ~\citet{Beaver1985} & Malaysia & lake  & 4,12,37 N & Yes   &       &  \\
      132   & ~\citet{GlobalWeb} & ~\citet{Beaver1985} & Malaysia & lake  & 4,12,37 N & Yes   &       &  \\
      133   & ~\citet{GlobalWeb} & ~\citet{Beaver1985} & Sri Lanka & lake  & 7,52,22 N & Yes   &       &  \\
      134   & ~\citet{GlobalWeb} & ~\citet{Beaver1985} & Madagascar & lake  & 19 S  & Yes   &       &  \\
      135   & ~\citet{GlobalWeb} & ~\citet{Beaver1985} & Seychelles & lake  & 4,40,46 S & Yes   &       &  \\
      136   & ~\citet{GlobalWeb} & ~\citet{Bradshaw1983} & USA   & lake  &       & No    & Could not locate original source &  \\
      137   & ~\citet{GlobalWeb} & ~\citet{Corker1984} & Hong Kong & lake  & 22,14-22,17 N & Yes   &       &  \\
      138   & ~\citet{GlobalWeb} & ~\citet{Kitching1983} & UK    & lake  &       & No    & Could not locate original source &  \\
      139   & ~\citet{GlobalWeb} & ~\citet{Kitching1983} & Australia & lake  &       & No    & Could not locate original source &  \\
      140   & ~\citet{GlobalWeb} & ~\citet{Siefert1979} & Venezuela & terrestrial & 10,21 N & Yes   &       &  \\
      141   & ~\citet{GlobalWeb} & ~\citet{Seifert1976} & Costa Rica & terrestrial &       & No    & Competition network &  \\
      142   & ~\citet{GlobalWeb} & ~\citet{Seifert1976} & Costa Rica & terrestrial &       & No    & Competition network &  \\
      143   & ~\citet{GlobalWeb} & ~\citet{Snow1958} & USA   & lake  & 34,41,45 N & Yes   &       &  \\
      144   & ~\citet{GlobalWeb} & ~\citet{Snow1958} & Germany & lake  &       & No    & Could not locate original source &  \\
      145   & ~\citet{GlobalWeb} & ~\citet{Rejmanek1979} & Europe & terrestrial &       & No    & Host-parasitoid web &  \\
      146   & ~\citet{GlobalWeb} & ~\citet{Rejmanek1979} & Europe & terrestrial &       & No    & Host-parasitoid web &  \\
      147   & ~\citet{GlobalWeb} & ~\citet{Rejmanek1979} & Europe & terrestrial &       & No    & Host-parasitoid web &  \\
      148   & ~\citet{GlobalWeb} & ~\citet{Rejmanek1979} & Europe & terrestrial &       & No    & Host-parasitoid web &  \\
      149   & ~\citet{GlobalWeb} & ~\citet{Force1974} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
      150   & ~\citet{GlobalWeb} & ~\citet{Hopkins1984} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
      151   & ~\citet{GlobalWeb} & ~\citet{Richards1926} & UK    & terrestrial & 51,20,04 N & Yes   &       &  \\
      152   & ~\citet{GlobalWeb} & ~\citet{Whittaker1984} & USA   & terrestrial &       & No    & Source web &  \\
      153   & ~\citet{GlobalWeb} & ~\citet{Mayse1978} & USA   & terrestrial & 40,06,38 N & Yes   &       &  \\
      154   & ~\citet{GlobalWeb} & ~\citet{Mayse1978} & USA   & terrestrial & 39,56,41 N & Yes   &       &  \\
      155   & ~\citet{GlobalWeb} & ~\citet{Askew1975} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
      156   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
      157   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
      158   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
      159   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
      160   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
      161   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
      162   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
      163   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
      164   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
      165   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
      166   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
      167   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
      168   & ~\citet{GlobalWeb} & ~\citet{Hawkins1984} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
      169   & ~\citet{GlobalWeb} & ~\citet{Hawkins1984} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
      170   & ~\citet{GlobalWeb} & ~\citet{Hawkins1984} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
      171   & ~\citet{GlobalWeb} & ~\citet{Hawkins1984} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
